The Quantum Sneakernet

### 2019-01-22 Simon's section/main.tex
Reformatted Sneakernet.bib

The first practical consideration for Sneakernet communications has been solved. Classical memories have fallen in price and increased in capacity to an even greater degree than transistor price and density. In 2018, Toshiba released a single 3.5-inch hard disk drive with a capacity of 14TB available for \$550 USD \href{https://www.amazon.com/Toshiba-14TB-SATA-7200RPM-Enterprise/dp/B07DHY61JP}{https://www.amazon.com/Toshiba-14TB-SATA-7200RPM-Enterprise/dp/B07DHY61JP}.

Let's contrast this capacity with fibre optic connections. In 2016 the new FASTER\index{FASTER} fibre optic communications link was brought online between northern California and Japan. Costing \$300m to deploy, it has a total data capacity of 7.5Tbps/s across the Pacific \href{https://www.nec.com/en/press/201408/global_20140811_01.html}{https://www.nec.com/en/press/201408/global_20140811_01.html}. Consequently, it takes two seconds, utilising the full design capacity of a \$300m dollar piece of telecommunications infrastructure, to transmit the data contained on a \$550 device that could fit into a handbag. This \$550 hard drive can be shipped via FedEx from northern California to Tokyo for about an extra \$150 and arrive about twenty hours later -- based on advertised prices from FedEx for door-to-door express shipping of a 1kg unit. Using that approach, we could achieve the same bandwidth as the FASTER network utilising approximately 36,000 hard drives shipped continuously back and forth. The total cost of this would be approximately \$20m dollars for the hard-drives and \$5m per day in commercial shipping costs (which could be made significantly cheaper by using more dedicated cargo transportation systems than FedEx, which is arguably the most expensive).

The capital cost alone associated with the FASTER network is \textit{fifteen} times more expensive than the capital cost of using hard drive-based Sneakernet. The operational costs of the hard drive system would be comparable if not lower than these fibre-optic links. So why do we spend so much time and money on capital and maintenance-intensive classical communications infrastructure such as submarine fibre or communications satellites (Fig.~\ref{fig:classical})?

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{classical}
	\caption{Satellite information from the Union of Concerned Scientists Satellite datebase \href{https://www.ucsusa.org/nuclear-weapons/space-weapons/satellite-database?_ga=2.192846958.535241894.1547878264-1715284942.1547878264#.XEK_gi1L1ro}{https://www.ucsusa.org/nuclear-weapons/space-weapons/satellite-database?_ga=2.192846958.535241894.1547878264-1715284942.1547878264#.XEK_gi1L1ro}.  Submarine optic cable data from wikipedia \href{https://en.wikipedia.org/wiki/List_of_international_submarine_communications_cables}{https://en.wikipedia.org/wiki/List_of_international_submarine_communications_cables}.  Global internet traffic sourced from \href{https://www.statista.com/statistics/499431/global-ip-data-traffic-forecast/}{https://www.statista.com/statistics/499431/global-ip-data-traffic-forecast/}.} \label{fig:classical}
\end{figure}

@@

How such a network will be used is less clear. As noted above, we can make the following arguments as to when a particular application `comes online':
\begin{itemize}
\item Authentication tokens can come online once the number of QMUs $> 1\times 10^2$. 
\item Key exchange can come online once the number of QMUs $> 10\times 10^3$.
\item One-time-pads can come online once the number of QMUs $> 50\times 10^6$. This assumes voice communications using the 600 bps NATO standard STANAG-4591 vocoding technique with a cumulative total of 10 hours of communication that needs to be encoded using QuSTICKS \href{https://www.public.navy.mil/jtnc/APIs/API_1.4_20150226_VocoderService.pdf}{https://www.public.navy.mil/jtnc/APIs/API_1.4_20150226_VocoderService.pdf}.
\item Direct coupling of fully error-corrected quantum computers at a MHz logic-gate rate once the number of QMUs $> 10\times 10^9$. 
\item Multi-link, global quantum internet once the number of QMUs $> 1\times 10^{12}$.
\end{itemize}

@@

\bibliography{sample}

>>>>

The first practical consideration for Sneakernet communications has been solved. Classical memories have fallen in price and increased in capacity to an even greater degree than transistor price and density. In 2018, Toshiba released a single 3.5-inch hard disk drive with a capacity of 14TB available for \$550 USD %\href{https://www.amazon.com/Toshiba-14TB-SATA-7200RPM-Enterprise/dp/B07DHY61JP}{https://www.amazon.com/Toshiba-14TB-SATA-7200RPM-Enterprise/dp/B07DHY61JP}.

Let's contrast this capacity with fibre optic connections. In 2016 the new FASTER\index{FASTER} fibre optic communications link was brought online between northern California and Japan. Costing \$300m to deploy, it has a total data capacity of 7.5Tbps/s across the Pacific %\href{https://www.nec.com/en/press/201408/global_20140811_01.html}{https://www.nec.com/en/press/201408/global_20140811_01.html}. Consequently, it takes two seconds, utilising the full design capacity of a \$300m dollar piece of telecommunications infrastructure, to transmit the data contained on a \$550 device that could fit into a handbag. This \$550 hard drive can be shipped via FedEx from northern California to Tokyo for about an extra \$150 and arrive about twenty hours later -- based on advertised prices from FedEx for door-to-door express shipping of a 1kg unit. Using that approach, we could achieve the same bandwidth as the FASTER network utilising approximately 36,000 hard drives shipped continuously back and forth. The total cost of this would be approximately \$20m dollars for the hard-drives and \$5m per day in commercial shipping costs (which could be made significantly cheaper by using more dedicated cargo transportation systems than FedEx, which is arguably the most expensive).

The capital cost alone associated with the FASTER network is 15 times more expensive than the capital cost of using hard drive-based Sneakernet. The operational costs of the hard drive system would be comparable if not lower than these fibre-optic links. So why do we spend so much time and money on capital and maintenance-intensive classical communications infrastructure such as submarine fibre or communications satellites (Fig.~\ref{fig:classical})?

\begin{figure}[htbp!]
	\includegraphics[clip=true, width=0.475\textwidth]{classical}
	%\caption{Satellite information from the Union of Concerned Scientists Satellite database \href{https://www.ucsusa.org/nuclear-weapons/space-weapons/satellite-database?_ga=2.192846958.535241894.1547878264-1715284942.1547878264#.XEK_gi1L1ro}{https://www.ucsusa.org/nuclear-weapons/space-weapons/satellite-database?_ga=2.192846958.535241894.1547878264-1715284942.1547878264#.XEK_gi1L1ro}.  Submarine optic cable data from wikipedia \href{https://en.wikipedia.org/wiki/List_of_international_submarine_communications_cables}{https://en.wikipedia.org/wiki/List_of_international_submarine_communications_cables}. Global internet traffic sourced from \href{https://www.statista.com/statistics/499431/global-ip-data-traffic-forecast/}{https://www.statista.com/statistics/499431/global-ip-data-traffic-forecast/}.} \label{fig:classical}
\end{figure}

@@

How such a network will be used is less clear. As noted above, we can make the following arguments as to when a particular application `comes online':
\begin{itemize}
\item Authentication tokens can come online once the number of QMUs $> 1\times 10^2$. 
\item Key exchange can come online once the number of QMUs $> 10\times 10^3$.
\item One-time-pads can come online once the number of QMUs $> 50\times 10^6$. This assumes voice communications using the 600 bps NATO standard STANAG-4591 vocoding technique with a cumulative total of 10 hours of communication that needs to be encoded using QuSTICKS %\href{https://www.public.navy.mil/jtnc/APIs/API_1.4_20150226_VocoderService.pdf}{https://www.public.navy.mil/jtnc/APIs/API_1.4_20150226_VocoderService.pdf}.
\item Direct coupling of fully error-corrected quantum computers at a MHz logic-gate rate once the number of QMUs $> 10\times 10^9$. 
\item Multi-link, global quantum internet once the number of QMUs $> 1\times 10^{12}$.
\end{itemize}

@@

\bibliography{sneakernet}
